---
title: "Iris Classification"
author: Anthony Ruiz
output: 
     revealjs::revealjs_presentation:
          fig_width: 6
          fig_height: 4
          theme: blood
          transition: concave
          center: true
---

## Motivation

<small>The motivation behind this project is to demonstrate some of my data science and R knowledge. As a disclaimer, I understand that business related data/questions are much more difficult to work on, however I unfortunately cant use business cases to publicly </small>


## Slide with Bullets
- This project/presentation has been created with the reveal package
- Bullet 2
- Bullet 3


## Slide with R Code and Output
```{r data import, message = FALSE}
iris_data <- read.csv("C:/Users/gexajr1/Desktop/Iris.csv")
```


## Packages used for modeling
```{r package installation, message = FALSE, warning = FALSE, fig.align='center'}
library(tidyverse)
library(knitr)
library(caret)
library(rattle)
library(dadva)
library(GGally)
library(stats)
```


## Data Exploration
```{r, message = FALSE, fig.align='center'}
ggpairs(iris_data[,2:6],mapping =aes(color = Species)) +
     theme_dadva()
```

##Summary Statistics
```{r Summary Statistics}
kable(summary(iris_data), align = 'c', caption = "Summary Statistics of Iris Data")
```

## Data Preperation
We want to split our data into training/testing datasets. We will use the training data to train the model and the testing set to test how our model performs on out of sample data.

```{r Data Processing}
set.seed(23)
iris_training <- sample_frac(iris_data,.85)
iris_testing <- setdiff(iris_data,iris_training)
```


## Recursive Partition (Decision Tree)
```{r Recursive Partion, fig.align = 'center'}

set.seed(23)
dt <- train(Species ~ SepalLengthCm + SepalWidthCm + PetalLengthCm + PetalWidthCm,
            method = "rpart", data = iris_training)

dt
```

## Model Output
```{r Decision Tree Output, fig.align = 'center'}
fancyRpartPlot(dt$finalModel, main = "Iris Classification - Recursive Partition Model", sub = "")
```


## Out of Sample Prediction
```{r}
dt_predictions <- predict(dt, newdata = iris_testing)
confusionMatrix(dt_predictions, iris_testing$Species)
```


## Viewing Incorrectly Classified Predictions
```{r}
test <- iris_testing %>%
          bind_cols(data.frame(dt_predictions)) %>%
          mutate(accurate_prediction = ifelse(Species == dt_predictions,"Correct","Incorrect"))
          

ggplot(data = test) +
     geom_point(mapping = aes(x = PetalLengthCm, y = PetalWidthCm, color = accurate_prediction))+
     theme_dadva()
```


##
```{r Kmeans Scree Plot, fig.align ='center', fig.height=6, fig.width=10}

kmean_cluster <- data.frame(1)

for(i in 1:15){
     kmean_cluster[i] <-  kmeans(iris_data[2:4], centers = i, nstart = 20)$tot.withinss
}

kmean_cluster <- kmean_cluster %>%
                 gather(1,"wss")

ggplot(data = kmean_cluster) +
     geom_line(mapping = aes(y = wss, x = 1:15)) +
     labs(y = "Within Sum of Squares", x = "Cluster Size", Main = "Scree Plot to Determine Optimal Cluster Size") +
     theme_dadva()

```
